Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-07 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Work on draft

        exposure_count <- exposure_data %>%
                dplyr::group_by(fips) %>%
                dplyr::summarize(count = n() /(end_year - start_year + 1)) %>%
                dplyr::rename(region = fips) %>%
                dplyr::mutate(region = as.numeric(region),
                              count = as.numeric(count)) %>%
                rbind(missing_counties)

        exposure_count$value <- cut(exposure_count$count, c(0, 
                                                            0.11,
                                                            0.22,
                                                            0.33,
                                                            0.44,
                                                            0.56,
                                                            0.67,
                                                            0.78,
                                                            0.89,
                                                            10),
                           labels = c("0-.10", ".11-.21",
                                      ".22-.32", ".33-.43",
                                      ".44-.55", ".56-.66",
                                      ".67-.77", ".78-.88", ".89+"),
                           include.lowest = TRUE)
        exposure_palette <- c("#FFFFFF", brewer.pal(8, name = "YlGnBu"))

@@

>>>>

        exposure_count <- exposure_data %>%
                dplyr::group_by(fips) %>%
                dplyr::summarize(count = 10 * n() /(end_year - start_year + 1)) %>%
                dplyr::rename(region = fips) %>%
                dplyr::mutate(region = as.numeric(region),
                              count = as.numeric(count)) %>%
                rbind(missing_counties)

        exposure_count$value <- cut(exposure_count$count, c(0, 
                                                            1,
                                                            2,
                                                            3,
                                                            4,
                                                            5,
                                                            6,
                                                            7,
                                                            8,
                                                            20),
                           labels = c("0-1", "1-2",
                                      "2-3", "3-4",
                                      "4-5", "5-6",
                                      "6-7", "7-8", "8+"),
                           include.lowest = TRUE)
        exposure_palette <- c("#FFFFFF", brewer.pal(8, name = "YlGnBu"))

@@

We assessed some statistics on the number of counties exposed to storms under different exposure metrics (Table \ref{tab:num_counties_exposed}).

```{r echo = FALSE, results = "asis"}
distance_exposure_50 <- county_distance(counties = my_fips, start_year = 1988,
                                     end_year = 2011, dist_limit = 50)
distance_exposure_75 <- county_distance(counties = my_fips, start_year = 1988,
                                     end_year = 2011, dist_limit = 75)
rain_exposure_125 <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 125, dist_limit = 500)
rain_exposure_175 <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 175, dist_limit = 500)
wind_exposure_20 <- county_wind(counties = my_fips, start_year = 1988,
                             end_year = 2011, wind_limit = 20)
wind_exposure_25 <- county_wind(counties = my_fips, start_year = 1988,
                             end_year = 2011, wind_limit = 25)

dist_exp <- distance_exposure %>%
        select(storm_id, fips) %>%
        mutate(dist_exposed = 1)
dist_exp_50 <- distance_exposure_50 %>%
        select(storm_id, fips) %>%
        mutate(dist_exposed_50 = 1)
dist_exp_75 <- distance_exposure_75 %>%
        select(storm_id, fips) %>%
        mutate(dist_exposed_75 = 1)
rain_exp <- rain_exposure %>%
        select(storm_id, fips) %>%
        mutate(rain_exposed = 1)
rain_exp <- rain_exposure %>%
        select(storm_id, fips) %>%
        mutate(rain_exposed = 1)
rain_exp_125 <- rain_exposure_125 %>%
        select(storm_id, fips) %>%
        mutate(rain_exposed_125 = 1)
rain_exp_175 <- rain_exposure_175 %>%
        select(storm_id, fips) %>%
        mutate(rain_exposed_175 = 1)
wind_exp <- wind_exposure %>%
        select(storm_id, fips) %>%
        mutate(wind_exposed = 1)
wind_exp_20 <- wind_exposure_20 %>%
        select(storm_id, fips) %>%
        mutate(wind_exposed_20 = 1)
wind_exp_25 <- wind_exposure_25 %>%
        select(storm_id, fips) %>%
        mutate(wind_exposed_25 = 1)

all_exp <- dist_exp %>%
        full_join(dist_exp_75, by = c("storm_id", "fips")) %>%
        full_join(dist_exp_50, by = c("storm_id", "fips")) %>%
        full_join(rain_exp, by = c("storm_id", "fips")) %>%
        full_join(rain_exp_125, by = c("storm_id", "fips")) %>%
        full_join(rain_exp_175, by = c("storm_id", "fips")) %>%
        full_join(wind_exp, by = c("storm_id", "fips")) %>%
        full_join(wind_exp_20, by = c("storm_id", "fips")) %>%
        full_join(wind_exp_25, by = c("storm_id", "fips")) %>%
        gather(metric, exposure, -storm_id, -fips) %>%
        mutate(exposure = !is.na(exposure))

flood_exposure <- county_events(counties = my_fips,
                              start_year = 1996, end_year = 2011,
                              event_type = "flood")
tornado_exposure <- county_events(counties = my_fips,
                              start_year = 1996, end_year = 2011,
                              event_type = "tornado")

flood_exp <- flood_exposure %>%
        select(storm_id, fips) %>%
        mutate(flood_exposed = 1)
tornado_exp <- tornado_exposure %>%
        select(storm_id, fips) %>%
        mutate(tornado_exposed = 1)

all_exp_2 <- flood_exp %>%
        full_join(tornado_exp, by = c("storm_id", "fips")) %>%
        gather(metric, exposure, -storm_id, -fips) %>%
        mutate(exposure = !is.na(exposure),
               storm_id = as.character(storm_id))  %>%
        dplyr::group_by(storm_id, metric) %>%
        dplyr::summarize(n_exposed = sum(exposure)) %>%
        dplyr::ungroup() %>%
        dplyr::group_by(metric) %>%
        dplyr::summarize(median_exposure = median(n_exposed),
                         iqr_exposure = paste(quantile(n_exposed, c(0.25, 0.75)),
                                              collapse = ", "), 
                         median_exposure = paste0(median_exposure, " (",
                                                  iqr_exposure, ")"),
                         max_exposure = max(n_exposed),
                         which_max_exposure = storm_id[which.max(n_exposed)],
                         which_max_exposure = gsub("-", ", ", which_max_exposure),
                         max_exposure = paste0(max_exposure, " (",
                                               which_max_exposure, ")"), 
                         n_100_plus = sum(n_exposed >= 100) / 10) %>%
        dplyr::select(-iqr_exposure, -which_max_exposure)

all_exp %>%
        dplyr::group_by(storm_id, metric) %>%
        dplyr::summarize(n_exposed = sum(exposure)) %>%
        dplyr::ungroup() %>%
        dplyr::group_by(metric) %>%
        dplyr::summarize(median_exposure = median(n_exposed),
                         iqr_exposure = paste(quantile(n_exposed, c(0.25, 0.75)),
                                              collapse = ", "), 
                         median_exposure = paste0(median_exposure, " (",
                                                  iqr_exposure, ")"),
                         max_exposure = max(n_exposed),
                         which_max_exposure = storm_id[which.max(n_exposed)],
                         which_max_exposure = gsub("-", ", ", which_max_exposure),
                         max_exposure = paste0(max_exposure, " (",
                                               which_max_exposure, ")"), 
                         n_100_plus = sum(n_exposed >= 100) / 10) %>%
        dplyr::select(-iqr_exposure, -which_max_exposure) %>%
        rbind(all_exp_2) %>%
        dplyr::mutate(metric = c("Distance (100 km or less)",
                                 "Distance (75 km or less)",
                                 "Distance (50 km or less)",
                                 "Rainfall (75 mm or more)",
                                 "Rainfall (125 mm or more)",
                                 "Rainfall (175 mm or more)",
                                 "Wind (15 m/s or more)",
                                 "Wind (20 m/s or more)",
                                 "Wind (25 m/s or more)",
                                 "Flood event",
                                 "Tornado event")) %>%
        xtable(caption = "County-level exposure statistics for different exposure metrics",
               label = "tab:num_counties_exposed",
               digits = c(0, 0, 0, 0, 1)) %>%
        print(include.rownames = FALSE, floating = TRUE,
              table.placement = "p", caption.placement = "top", 
              booktabs = TRUE, comment = FALSE, timestamp = NULL)
```
